biological data preperation

### 2018-09-11 src/biological_data_prep.Rmd
addition of "see who sampled in which year"
addition of month by instituion

>>>>

# see who sampled in which year and month

year
```{r}
inst_by_yr <- with(adddata, table(year, institutioncode))
write.csv(inst_by_yr, file = "../output/bio/institutioncode_by_yr.csv")
```

month
```{r}
inst_by_mt <- with(adddata, table(month, institutioncode))
write.csv(inst_by_mt, file = "../output/bio/institutioncode_by_mth.csv")
```
